\Large \bf Module Dialysis with Lya

### 2019-12-20 paper/draft.tex
Update abstract

This paper introduces \emph{module dialysis}, a novel technique for dynamic analysis specifically tailored to module boundaries. % to applications with many modules
Modules are becoming the cornerstone of modern software engineering:
  applications today use hundreds of modules, to the point where code written by their nominal developers is becoming only a small fraction of their total line count.
On the surface, such code reuse is beneficial, as it lowers development costs, software testing, encapsulation; 
  however, such over-reliance creates many challenges later in the development process, exactly because developers have little knowledge and understanding of module's internals.
For example, security auditing and performance profiling---which are already challenging for monolithic applications---become extremely difficult in the presence of deeply-nested third-party code.

% Turn such over-reliance on its head
To address these challenges, module dialysis enables dynamic fragmentation, analysis, and re-assembly of applications at the level of individual modules.
One of its highlights is ease of deployment and use:
  (i) bolted onto existing runtime environments as a library, by wrapping and transforming the underlying module system
  (ii) allowing developers to extract information using the same abstractions as the host language---eschewing low-level instrumentation.
Due to the in the host language and at a coarser granularity than full-fledged dynamic analysis, module dialysis has the potential of low performance overheads while still providing important information.

@@

Module dialysis can be bolted on existing language runtime environments in a language-agnostic fashion 
% By leveraging the ubiquity of third-party modules in today's applications
Such modules can be part of third-party packages or of the language's standard library;
  the latter is important for resources that are part of the broader environment where the application is executing, such as the operating system and the network.
By leveraging the ubiquity of third-party modules in today's applications, this analysis provides insights k

We use a series of case-study analyses to motivate \sys's design and demonstrate how \sys provides high-performance by shadowing variables and transforming and wrapping values

, all with minimal developer effort.
The key feature is that module-level analysis can be bolted onto existing runtime environments as a library, without requiring low-level intsrumentation and maintaing the semantics of..
Measurements of two COWL implementations, one in Firefox and one in Chromium, demonstrate a virtually imperceptible increase in page-load latency.

>>>>

This paper introduces \emph{library dialysis}, a novel dynamic-analysis technique specifically tailored to applications with many third-party libraries.
The proliferation of third party libraries in applications is a recent trend in software engineering:
Libraries are becoming the cornerstone of modern 
  applications today rely on hundreds of libraries, to the point where code written by their nominal developers is becoming only a small fraction of their total line count.
% On the surface, such reliance is beneficial, as it lowers development costs, aids targeted software testing, and enables code reuse;
Despite its benefits, such over-reliance creates many challenges down the road, exactly because developers have little knowledge and understanding of each library's internals.
For example, security auditing and performance profiling---which are already challenging for monolithic applications---become extremely difficult in the presence of deeply-nested third-party code.

To address these challenges, library dialysis enables dynamic fragmentation, analysis, and re-assembly of applications at the level of individual modules.
One of its highlights is ease of deployment and use:
  (i) bolted onto existing runtime environments as a library, by wrapping and transforming the underlying module system
  (ii) allowing developers to extract information using the same abstractions as the host language---eschewing low-level instrumentation.
Due to the in the host language and at a coarser granularity than full-fledged dynamic analysis, module dialysis has the potential of low performance overheads while still providing important information.

@@

Module dialysis can be bolted on existing language runtime environments in a language-agnostic fashion 
% By leveraging the ubiquity of third-party modules in today's applications
Such modules can be part of third-party packages or of the language's standard library;
  the latter is important for resources that are part of the broader environment where the application is executing, such as the operating system and the network.

, all with minimal developer effort.
As a result,
